---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(warning = FALSE,
  collapse = TRUE,
  comment = "#>",
fig.path = "man/figures/",
out.width = "100%"
)
```

## Package overview
Functions to find a short and accurate decision rule in disjunctive normal form using the Exhaustive Procedure for LOgic-Rule Extraction (EXPLORE) algorithm. The application performs and exhaustive search on all Boolean Normal Form decision rules.

## Package installation

You can install the latest version of EXPLORE like so:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("mi-erasmusmc/EXPLORE")
```

Additional instructions: to be added.


## Example usage using iris dataset
```{r}
library(Explore)
library(farff)
```

Load data:
```{r, eval=FALSE}
data <- farff::readARFF(system.file("examples/iris.arff", package = "Explore"))
output_path <- file.path(getwd(), "output//")
```

Fit model with defaults and/or input parameters:
```{r, eval=FALSE}
model <- Explore::trainExplore(output_path = output_path, 
                               file_name = "iris", 
                               train_data = data, 
                               ClassFeature = "'class'", 
                               PositiveClass = '"Iris-versicolor"')
```
  
Predict:
```{r, eval=FALSE}
prediction <- Explore::predictExplore(model, test_data = data)
```  


Additional documentation includes:
- Vignette code examples in combination with PLP: [to be added](~/Documents/Git/Explore/vignettes/EXPLORE_withPLP.Rmd) 
- Package manual: [to be added](~/Documents/Git/Explore/vignettes/Explore_1.0.pdf) 


## Development status
EXPLORE is under active development.


## Publication
Rijnbeek, P.R., Kors, J.A. Finding a short and accurate decision rule in disjunctive normal form by exhaustive search. Machine Learning 80, 33–62 (2010). https://doi.org/10.1007/s10994-010-5168-9
